Stat 400 Presentation

### 2021-12-16 Paper.Rmd
Made some minor adjustments

Background:
The paper "Novel approach for Monte Carlo simulation of the new COVID-19 spread dynamics" aims to investigate the transmission and incubation random processes of Covid-19. The goal of the study is to generate epidemiological data based on the natural mechanisms of transmission of the virus assuming random interactions of a large-finite number of subjects in very short distances. A few important assumptions were made in how the transmission of the virus occurs when the physical distance between subjects decreases, so that the probability of transmission converges to one as the distance between subjects goes to zero. Their model defined the steps of movement in a defined space as a random process. They approached this through the SIR model; A model defining Susceptible, Infected, and Recovered individuals. Any change in the SIR model is based on time, as the function iterates through a set number of days. They started with a 0.5% infection rate and simulated daily infection counts over a number of days. In order to capture the many factors in transmission, including the relationship between infection probability and physical distance, effective and ineffective mask wearing, and environmental conditions they distributed these factors Exponential(rate = lambda). Initial recovery and incubation times were distributed Gamma($\alpha$, $\beta$) [1].

@@

All the above culminates in the simulator function. This function takes in the given area, number of subjects, number of starting infected subjects, mean infection distance, number of days for the simulation, and proportion of subjects that are vaccinated as arguments. Using a for loop for each day, the function generates new positions for the subjects, and returns how many people have been infected per day. This can be used to generate a plot for the number of daily cases by plotting day on the x axis and number of cases on the y axis. If you run the simulation repeatedly, you can create a bootstrap confidence interval for the mean number of cases each day. This is done in the get_bootstrap_cis function. The function returns the bootstrap confidence intervals as well as the mean for each day, for a given sample size. For our purposes we used a sample size of 20 due to the computational burden of repeatedly running simulations. This data can be used to create a plot of the mean number of cases per day as well as 95% bootstrap confidence intervals for each day. We decided to use percentile bootstrap confidence intervals since they are the most interpretable.

@@

```{r, echo=FALSE}
set.seed(400)
plot_dat1 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0)

@@

plot_dat2 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0.5)

@@

plot_dat3 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0.8)

@@

plot_dat4 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0.95)

>>>>

Background:
The paper "Novel approach for Monte Carlo simulation of the new COVID-19 spread dynamics" aims to investigate the transmission and incubation random processes of Covid-19. The goal of the study is to generate epidemiological data based on the natural mechanisms of transmission of Covid-19 assuming random interactions between subjects. A few important assumptions were made in how the transmission of Covid-19 occurs when the physical distance between subjects decreases, so that the probability of transmission converges to one as the distance between subjects goes to zero. Their model defined the steps of movement in a defined space as a random process. They approached this through the SIR model; A model defining Susceptible, Infected, and Recovered individuals. Any change in the SIR model is based on time, as the function iterates through a set number of days. They started with a 0.5% infection rate and simulated daily infection counts over a number of days. In order to capture the many factors in transmission, including the relationship between infection probability and physical distance, effective and ineffective mask wearing, and environmental conditions they distributed these factors Exponential(rate = lambda). Initial recovery and incubation times were distributed Gamma($\alpha$, $\beta$) [1].

@@

All the above culminates in the simulator function. This function takes in the given area, number of subjects, number of starting infected subjects, mean infection distance, number of days for the simulation, and proportion of subjects that are vaccinated as arguments. Using a for loop for each day, the function generates new positions for the subjects, and returns how many people have been infected per day. This can be used to generate a plot for the number of daily cases by plotting day on the x axis and number of cases on the y axis. If you run the simulation repeatedly, you can create a bootstrap confidence interval for the mean number of cases each day. This is done in the get_bootstrap_cis function. The function returns the bootstrap confidence intervals as well as the mean for each day, for a given sample size. For our purposes we used sample sizes of 20 and 30 due to the computational burden of repeatedly running simulations. This data can be used to create a plot of the mean number of cases per day as well as 95% bootstrap confidence intervals for each day. We decided to use percentile bootstrap confidence intervals since they are the most interpretable.

@@

```{r, echo=FALSE}
set.seed(400)
plot_dat1 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=30, prop_vac = 0)

@@

plot_dat2 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=30, prop_vac = 0.5)

@@

plot_dat3 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=30, prop_vac = 0.8)

@@

plot_dat4 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=30, prop_vac = 0.95)

### 2021-12-16 Stat 400 presentation.Rmd
Made some minor adjustments

- The goal of the study is to generate epidemiological data based on the natural mechanism's of transmission of the virus assuming random interactions of a large-finite number of individuals in very short distance ranges.

@@

- The transmission of the virus occurs when the physical distance between individuals decreases to where the probability of transmission converges to one, asymptotmically.

- the step of movement of people is a randomly assigned process.

- the specific parameters of focus will be recovery and incubation time.

>>>>

- The goal of the study is to generate epidemiological data based on the natural mechanisms of transmission of the virus assuming random interactions of subjects in a confined space.

@@

- The transmission of the virus occurs when the physical distance between individuals decreases to where the probability of transmission converges to one, as the distance between subjects goes to zero.

- The step of movement of people is a randomly assigned process.

- The specific parameters of focus will be recovery and incubation time.
